---
title: "485_Project"
author: "LinhanHu;Ruike Li"
date: "April 23, 2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup}
library(readr)
X <- read_csv("C:/Users/sur/Desktop/Financial project/X_variable _new.csv", 
    col_types = cols(Date = col_date(format = "%m/%d/%Y")))

Y <- read_csv("C:/Users/sur/Desktop/Financial project/Y_variable/Y/AEIS.csv", 
    col_types = cols(Date = col_date(format = "%m/%d/%Y")))

```

## Multiple regression model checking
In its simplest form, a multiple linear regression model is a valid model for the data if the conditional mean of Y given X is a linear function of X and the conditional variance of Y given X is constant. In other words,  
$E(Y|X=x) = \beta_0+\beta_1x_1+\beta_2x_2+\beta_3x_3+\beta_4x_4+...+\beta_px_p$ and $Var(Y|X = x) = \sigma^2$  
When a valid model has been fit, a plot of standardized residuals, $r_i$ against any predictor or any linear combination of the predictors (such as the fitted values) will have the following features:
*A random scatter of points around the horizontal axis, since the mean function
of the $e_i$ is zero when a correct model has been fit
*Constant variability as we look along the horizontal axis  

An implication of these features is that **any pattern in a plot of standardized
residuals is indicative that an invalid model has been fit to the data**. 

```{r cars}
#Full model.
m1 <- lm(Y$Open~Y$High+Y$Low+Y$Close+Y$Volume+Y$Report_Released+Y$Positive+Y$Negative+Y$beta+Y$`p/e`+X$USD_RMB+X$USD_EUR+X$USD_JYP+X$payday+X$`interest rate`+X$Oil_price)
summary(m1)

m2 <- lm(Y$Open~Y$Volume+Y$Report_Released+Y$Positive+Y$Negative+Y$beta+Y$`p/e`+X$USD_RMB+X$USD_EUR+X$USD_JYP+X$payday+X$`interest rate`+X$Oil_price)
summary(m2)

pairs(Y$Open~Y$High+Y$Low+Y$Close+Y$Volume+Y$Report_Released+Y$Positive+Y$Negative+Y$beta+Y$`p/e`+X$USD_RMB+X$USD_EUR+X$USD_JYP+X$payday+X$`interest rate`+X$Oil_price)
```
```{r 2}
plot(m2)
abline(v=2*13/756,lty=2)
```
#Correlations between the predictors
```{r 1}
A <- cbind(Y$Volume,Y$Report_Released,Y$Positive,Y$Negative,Y$beta,Y$`p/e`,X$USD_RMB,X$USD_EUR,X$USD_JYP,X$payday,X$`interest rate`,X$Oil_price)
c <- cor(A)
round(c,3)
```

## Plots of standardized residuals against each predictor and the fitted values

```{r pressure}
StanRes1 <- rstandard(m2)
par(mfrow=c(2,2))
plot(Y$Volume,StanRes1, ylab="Standardized Residuals",xlab = "Volume")
boxplot(StanRes1~Y$Report_Released, ylab="Standardized Residuals",xlab = "Report_Released")
boxplot(StanRes1~Y$Positive, ylab="Standardized Residuals",xlab = "Positive")
boxplot(StanRes1~Y$Negative, ylab="Standardized Residuals",xlab ="Negative")
plot(Y$beta,StanRes1, ylab="Standardized Residuals",xlab = "beta")
plot(Y$`p/e`,StanRes1, ylab="Standardized Residuals",xlab = "p/e ratio")
plot(X$USD_RMB,StanRes1, ylab="Standardized Residuals",xlab = "USD_RMB")
plot(X$USD_EUR,StanRes1, ylab="Standardized Residuals",xlab = "USD_EUR")
plot(X$USD_JYP,StanRes1, ylab="Standardized Residuals",xlab = "USD_JYP")
boxplot(StanRes1~X$payday, ylab="Standardized Residuals",xlab ="payday")
plot(X$`interest rate`,StanRes1, ylab="Standardized Residuals",xlab = "Interest")
plot(X$Oil_price,StanRes1, ylab="Standardized Residuals",xlab = "Oil price")
plot(m2$fitted.values,StanRes1, ylab="Standardized Residuals",xlab="Fitted Values")

```


##Added-Variable Plot
```{r step 2}
library(car)
avPlot(m2,variable=Y$Volume,ask=FALSE)
avPlot(m2,variable=Y$Report_Released,ask=FALSE)
avPlot(m2,variable=Y$Positive,ask=FALSE)
avPlot(m2,variable=Y$Negative,ask=FALSE)
avPlot(m2,variable=Y$beta,ask=FALSE)
avPlot(m2,variable=Y$`p/e`,ask=FALSE)
avPlot(m2,variable=X$USD_RMB,ask=FALSE)
avPlot(m2,variable=X$USD_EUR,ask=FALSE)
avPlot(m2,variable=X$USD_JYP,ask=FALSE)
avPlot(m2,variable=X$payday,ask=FALSE)
avPlot(m2,variable=X$`interest rate`,ask=FALSE)
avPlot(m2,variable=X$Oil_price,ask=FALSE)

```

##Inverse response plot
```{r step 3}
library(alr3)
inverse.response.plot(m2,key=TRUE)
```

## Log-likelihood for the Box-Cox transformation method
```{r step 4}
library(MASS)
boxcox(m2,lambda=seq(-0.6,0,length=20))
```

```{r step 5}
m3 <- update(m2, subset=(1:756)[-c(756)])
summary(m3)
plot(m3)
abline(v=2*13/755,lty=2)
```

## Model selection 
Conduct F- test to see if the coefficient is 0.
```{r step 6}
anova(m2)  ## conduct F- test to see if the coefficient is 0

summary(powerTransform(m2))
```

```{r 3}

Z=merge(X, Y, sort = FALSE)
attach(Z)
```



Use leaps to determine which variable we should have.
```{r step 7}
#A <- cbind(Y$Volume,Y$Report_Released,Y$Positive,Y$Negative,Y$beta,Y$`p/e`,X$USD_RMB,X$USD_EUR,X$USD_JYP,X$payday,X$`interest rate`,X$Oil_price)
B = cbind(Volume,Report_Released,Positive, Negative, beta, Z$`p/e` ,USD_EUR,USD_JYP, USD_RMB, payday,Z$`interest rate`, Oil_price)

library(leaps)
b = regsubsets(as.matrix(B),Open)
rs <- summary(b)
par(mfrow=c(1,1))
plot(1:8,rs$adjr2,xlab="Subset Size",ylab="Adjusted R-squared")

#subsets(b,statistic=c("adjr2"))
```

Using AIC, BIC, AICC to choose reduced model.
```{r step 8}
om1 <- lm(Y$Open~X$Oil_price)
om2 <- lm(Y$Open~X$Oil_price+X$`interest rate`)
om3 <- lm(Y$Open~X$Oil_price+X$`interest rate`+X$USD_RMB)
om4 <- lm(Y$Open~X$Oil_price+X$`interest rate`+X$USD_RMB+X$USD_EUR)
om5 <- lm(Y$Open~X$Oil_price+X$`interest rate`+X$USD_EUR+Y$Negative)
om6 <- lm(Y$Open~X$Oil_price+X$`interest rate`+X$USD_EUR+Y$Negative +Y$Positive)
#Y$Open~Y$Volume+Y$Report_Released+Y$Positive+Y$Negative+Y$beta+Y$`p/e`+X$USD_RMB+X$USD_EUR+X$USD_JYP+X$payday+X$`interest rate`+X$Oil_price
#Calculate AIC
extractAIC(om1,k=2)
extractAIC(om2,k=2)
extractAIC(om3,k=2)
extractAIC(om4,k=2)
extractAIC(om5,k=2)
extractAIC(om6,k=2)
#Calculate AICc
n <- length(om1$residuals)
npar <- length(om1$coefficients) +1
extractAIC(om1,k=2)+2*npar*(npar+1)/(n-npar-1)
npar <- length(om2$coefficients) +1
extractAIC(om2,k=2)+2*npar*(npar+1)/(n-npar-1)
npar <- length(om3$coefficients) +1
extractAIC(om3,k=2)+2*npar*(npar+1)/(n-npar-1)
npar <- length(om4$coefficients) +1
extractAIC(om4,k=2)+2*npar*(npar+1)/(n-npar-1)
npar <- length(om5$coefficients) +1
extractAIC(om5,k=2)+2*npar*(npar+1)/(n-npar-1)
npar <- length(om6$coefficients) +1
extractAIC(om6,k=2)+2*npar*(npar+1)/(n-npar-1)

#Calculate BIC
extractAIC(om1,k=log(n))
extractAIC(om2,k=log(n))
extractAIC(om3,k=log(n))
extractAIC(om4,k=log(n))
extractAIC(om5,k=log(n))
extractAIC(om6,k=log(n))

```

**base on AIC, AICC and BIC, we will choose model 4,which contains Oil_price,interest.rate,USD_RMB,USD_EUR**

use backward selection based on AIC
```{r step 9}
om7 = m2
backAIC <- step(om7,direction="backward")
###########use backward selection based on BIC
backBIC <- step(om7,direction="backward",k = log(n))
###########Forward selection based on AIC
mint <- lm(Open~1,data=Z)
x1 = Volume
x2 = Report_Released
x3 =Positive
x4 = Negative
x5 = beta
x6 = Z$`p/e`
x7 = JYP_USD
x8 = USD_RMB
x9 = USD_EUR
x10 = USD_JYP
x11 = payday
x12 = Z$`interest rate`
x13 =Oil_price

forwardAIC <- step(mint,scope=list(lower=~1,
  upper=~x1+x2+x3+x4+x5+x6+x7+x8+x9+x10+x11+x12+x13),
  direction="forward", data=Z)

###Forward selection based on BIC
forwardBIC <- step(mint,scope=list(lower=~1,
  upper=~x1+x2+x3+x4+x5+x6+x7+x8+x9+x10+x11+x12+x13),
  direction="forward", data=Z,k=log(n))
#### the model choose the x8 + x12 + x9 + x13 + x4
```

#Based on the above method, we finally choose a 6 variable model with independent variables:Positive, Negative, Oil price, Interest rate, USD_RMB, USD_EUR
```{r step 10}
m5=lm(Y$Open~Y$Positive+Y$Negative+X$USD_RMB+X$USD_EUR+X$`interest rate`+X$Oil_price)

summary(m5)
pairs(Y$Open~Y$Positive+Y$Negative+X$USD_RMB+X$USD_EUR+X$`interest rate`+X$Oil_price)
C <- cbind(Y$Positive,Y$Negative,X$USD_RMB,X$USD_EUR,X$`interest rate`,X$Oil_price)
c <- cor(C)
round(c,3)
plot(m5)

abline(v=2*7/756,lty=2)

StanRes2 <- rstandard(m5)
par(mfrow=c(2,2))

boxplot(StanRes2~Y$Positive, ylab="Standardized Residuals",xlab = "Positive")
boxplot(StanRes2~Y$Negative, ylab="Standardized Residuals",xlab ="Negative")
plot(X$USD_RMB,StanRes2, ylab="Standardized Residuals",xlab = "USD_RMB")
plot(X$USD_EUR,StanRes2, ylab="Standardized Residuals",xlab = "USD_EUR")
plot(X$`interest rate`,StanRes2, ylab="Standardized Residuals",xlab = "Interest")
plot(X$Oil_price,StanRes2, ylab="Standardized Residuals",xlab = "Oil price")
plot(m5$fitted.values,StanRes2, ylab="Standardized Residuals",xlab="Fitted Values")


avPlot(m2,variable=Y$Positive,ask=FALSE)
avPlot(m2,variable=Y$Negative,ask=FALSE)
avPlot(m2,variable=X$USD_RMB,ask=FALSE)
avPlot(m2,variable=X$USD_EUR,ask=FALSE)
avPlot(m2,variable=X$`interest rate`,ask=FALSE)
avPlot(m2,variable=X$Oil_price,ask=FALSE)
```

##"Tuning" models
Randomly split the whole dataset into 70 percent for training and 30 percent for testing. Using a usual least squares
linear regression model, fit to the training data:
```{r step 11}
library(caTools)
set.seed(101) 
sample = sample.split(Z$Date, SplitRatio = .70)
train = subset(Z, sample == TRUE)
test  = subset(Z, sample == FALSE)

attach(train)
m6=lm(Open~Positive+Negative+USD_RMB+USD_EUR+`interest rate`+Oil_price)
sm=summary(m6)
sm
detach(train)
```

Since MSE measures the average of the squares of the errors or deviations-that is, the difference between the estimator and what is estimated, we use MSE to identify the accuracy of our model.  
$MSE=\frac{1}{n} \sum_{i=1}^n (\hat{y_i}-y_i)^2$   
Compute the MSE of model when applied to the training data and to the testing data:
```{r step 12}
#Report the MSE of model when applied to the training data.
mse <- function(sm) {
  mean(sm$residuals^2)
}
mse(sm)

#Report the MSE of your model when applied to the testing data. 
y_hat <- predict(m6, test)
y=test$Open
mean((y_hat-y)^2)
```
```{r step 13}
library(caret)
# define training control
#train_control <- trainControl(method="repeatedcv", number=10, repeats=3)
# train the model
#model <- train(Open~Positive+Negative+USD_RMB+USD_EUR+`interest rate`+Oil_price, data=Z, trControl=train_control, method="nb")
# summarize results
#print(model)
```

##Time series data
It is common statistical practice to look at values of the correlation between $Y$ and the various values of lagged $Y$ for different periods.  
Such values are called **autocorelations**:  
$Autocorrelation(l)=\frac{\sum_{t=l+1}^n(y_t-\hat{y})(y_{t-l}-\hat{y})}{\sum_{t=1}^n(y_t-\hat{y})^2}$

```{r step 14}
attach(Z)
acf(Open)
```

The dashed lines correspond to $-2/\sqrt{n}$ and $2/\sqrt{n}$, since autocorrelations are declared to be statistically significantly different from zero.